Application of a Cut-Cell Immersed Boundary Method for Wildfire Simulation over Complex Terrain

### 2020-12-08 Response_to_Reviewer_1.tex

\documentclass[12pt]{article}

\setlength{\textwidth}{6.25in}
\setlength{\textheight}{8.75in}
\setlength{\topmargin}{0.in}
\setlength{\headheight}{0.in}
\setlength{\headsep}{0.in}
\setlength{\parindent}{0.in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\parskip}{\baselineskip}
\setlength{\leftmargini}{\parindent} % Controls the indenting of the "bullets" in a list

\usepackage{xcolor}
\newcommand\hl[1]{\textcolor{red}{#1}}

\pagestyle{empty}

\begin{document}

\begin{center}
{\bf Response to comments by Reviewer 1}
\end{center}

The article "Application of a Cut-Cell Immersed Boundary Method for Wildfire Simulation over
Complex Terrain" is clearly written and well structured. It shows noticeable effort to describe an
original immersed boundary method, which is the core of its purpose. However, it is difficult to
assess the relevance of this work, for three main reasons.

\hl{Our original intent was to present a broad overview of the our approach to modeling wildland fire. The technical details of the model, verification and validation, and a user's guide is part of the package that one downloads when using the model, and these documents are available at the model web site. Nevertheless, we have added more details to the paper to better describe our approach.}

1. A lack of model description

The IBM together with the main solved PDE are correctly presented and a large amount of
previous articles globally allows understanding the demarch. But many submodels and
parametrization choices, that may have a strong influence on the final result, are weakly
depicted. In particular:

The volume combustion source term is not described.

\hl{A new section (Sec.~2.2 ``Subgrid Parameterizations'') discusses subgrid parameterizations and combustion details.}

Radiative modelling in the thermal divergence equation is not given. In particular, indications
should be given on the gas and soot absorption coefficients, if required, or on a radiative fraction

\hl{Further details on the radiation model have been added.}

The pyrolysis model used for the lagrangian particles or the porous boundary is not given. In
particular, the pyrolysis model shape (volume model ? surface model ?) is not depicted, and
neither the chemical degradation path for the pyrolysing vegetation, nor the mass and heat
transfer models in the porous boundary or the solid particles, are explained, whereas all these
aspects may have a strong influence on the mass of fuel released in the atmosphere, and therefore
on the fire spread rate.

\hl{Details of the pyrolysis model have been added.}

The heat exchange modelling between the gas phase and the solid particles is not depicted.

\hl{Details have been added.}

Same problem for many semi-empirical coefficients used for fluid/solid interface models: the
drag coefficient and the shape factor in the drag force model (they probably differ between the
particle model and the boundary flux model since they do not consider the same solid objects),
the Nusselt correlation for the heat exchange coefficient.

\hl{We added more details about how the convective and radiative heat transfer is done for the particle and boundary fuel models.}

2. The influence of the numerical model parameters

A sensitivity analysis on (at least) the following parameters would be helpful to assess the
relevance of the numerical model:

grid cell size

\hl{The flat terrain fire spread (CSIRO) cases were all run at three different grid resolutions and showed no significant difference in spread rate. }

pyrolysis model parameters, more precisely those which are made under an a priori assumption
(conductivity, specific heat)

\hl{We added a reference to a paper that McGrattan wrote in 2017 for the U.S. Combustion Institute meeting on sensitivity of parameters in the particle-based CSIRO calculations}

Obukhov length and roughness length

In particular, a comparison with the parameters used in a previous study [22] would be
interesting, insofar as the model seems to be very close, except on the management on the
boundary condition.

\hl{Physical parameters describing the vegetation in the Australian grass land experiments are the same in the current study and the past study. However, many aspects of the modeling approach have changed or advanced, making it difficult to make useful comparisons regarding the influence of some model parameters or methods. These include the modeling approach for the ambient wind. This is discussed in the text.}

3. A lack of quantitative comparisons

In section 6.1, the only quantitative comparison is made on the average fire rate of spread. But,
similarly with Ref [22], many comparisons could be made:

Mass loss rate/heat release rate time histories

fire front positions

velocity in the low atmospheric layer

\hl{We added more details about the flat terrain fire spread simulations, in particular a two-dimensional comparison of the fire front versus aerial observations.}

All these comparisons between the two first approaches and the previous work could bring
important information to explain the observed discrepancies: in particular, if these differences
are explained by interface heat transfer issues, or pyrolysis model issues.

\hl{We understand the reviewer's point. The differences between the current model and the version of the model in Mell et al.(2007) could, potentially, shed light on physical processes that need model advancements, such as heat transfer or thermal degradation. However, there are numerous differences between the 2007 and the current version of the model and these prohibitively confound such a comparison.}

Finally, section 6.2 is of poor interest, because no reason for the differences between the actual
fire and the simulation is raised, and no comparison with other numerical tools is given.

\hl{Kevin}

To conclude with, this paper needs strong improvements in the model description, the
consideration of the effects of uncertainties related to model parametrization on the numerical
results, and in the quantitative description of the results and the differences between the
numerical model. In particular, it should include a precise comparison with simulations of ref.
[22], since the observed differences cannot be related, at this stage, to the implementation of the
IBM or to differences in the model description or parametrization. In this respect, the interest of
the IBM approach, which is the main originality of this paper, is not shown.

\end{document}

### 2020-12-08 Response_to_Reviewer_2.tex

\documentclass[12pt]{article}

\setlength{\textwidth}{6.25in}
\setlength{\textheight}{8.75in}
\setlength{\topmargin}{0.in}
\setlength{\headheight}{0.in}
\setlength{\headsep}{0.in}
\setlength{\parindent}{0.in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\parskip}{\baselineskip}
\setlength{\leftmargini}{\parindent} % Controls the indenting of the "bullets" in a list

\usepackage{xcolor}
\newcommand\hl[1]{\textcolor{red}{#1}}

\pagestyle{empty}

\begin{document}

\begin{center}
{\bf Response to comments by Reviewer 2}
\end{center}

Early attempts at a mechanistic modeled wildfire spread was in the late 1960s. After these few
years of active development and advancement a lagged occurred for 15 to 20 years. The early.
development was generally due to two engineers Rothermel and Albini. The delay was caused
by the fact that a mechanistic approach is not in the training background for most Foresters. In
the 1980s with the major advances in numerical techniques applied to combustion and fluid
dynamics the gap with the Forester’s got even larger. However, in the last few decades
engineers and fluid dynamicists have stepped in and made important progress. We are now at a
stage where mechanistic models are becoming common and designed for different needs of
wildfire managers.

This paper is one of these developments. It uses large eddy simulations in the Fire Dynamic
Simulator using three ways of describing the fuel and fire spread: fuel as a range of Lagrangian
particles, fuel as a porous media and the traditional (empirical) fire boundary from which the
fire spreads, the so-called level set approach. The arguments in the paper is well-developed
using a novel boundary technique—cut- cell immersed method. Considering the sophistication
of the rest of the model the assimilation technique used seems to be very simplistic and I
assume temporary. Wind is such an important process in wildfires one assumes that this will be
better developed. Overall, I found the model section difficult but very exciting.

\hl{Since the time of the initial manuscript submission a significant improvement has been made in the way we treat wind boundary conditions.  As the reviewer noted, the previous approach was a rudimentary form of data assimilation where nudging was was used for momentum throughout the computational domain.  On closer inspection of wind validation cases we discovered two significant issues with this approach: First, the forcing terms did not work well together with the ``open'' boundary conditions we were using at the time for inflow and outflow convective boundaries---unstable inflow waves would persist if any flow reversals due to turbulence were encountered.  Second, the forcing terms in the momentum equation were clearly suppressing turbulence on the leeward side of hills. \\ \\
To overcome these issues we have developed an improved ``open'' boundary condition, which is described in the revised manuscript (Sec.~5 on ``Atmospheric Wind Boundary Conditions'').  This new boundary condition solves both of the problems mentioned above, it is easier to implement, and it still allows for one-way downscaling of microscale meteorological model output or weather observations.  However, as the reviewer alludes, a more advanced modeling approach would allow for the possibility of a two-way coupling with the at least the microscale (1 km), but also the mesoscale (10 km) meteorologic models.  This is presently beyond our scope, but something we are considering for future work.}

The numerical experiments are important to show how the model works with real properties.
However, they seem to be an add-on and not very well developed and discussed. Something
needs to be done with this section to make it as important part of the rest of the paper.

\hl{More detail has been added to the numerical examples.}

The idea of putting the scale differences together in the model boundary seems to be a very
useful advance.

\hl{The new ``open'' boundary conditions are capable of utilizing a synthetic eddy method to superimpose turbulence length scales on the background mean flow profiles.  A small example case is provided as a proof of concept.  We plan to explore the affect of inflow turbulence in more depth as future work.}

\end{document}

### 2020-12-08 Response_to_Reviewer_3.tex

\documentclass[12pt]{article}

\usepackage{amsmath}

\setlength{\textwidth}{6.25in}
\setlength{\textheight}{8.75in}
\setlength{\topmargin}{0.in}
\setlength{\headheight}{0.in}
\setlength{\headsep}{0.in}
\setlength{\parindent}{0.in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\parskip}{\baselineskip}
\setlength{\leftmargini}{\parindent} % Controls the indenting of the "bullets" in a list

\usepackage{xcolor}
\newcommand\hl[1]{\textcolor{red}{#1}}

\pagestyle{empty}

\begin{document}

\begin{center}
{\bf Response to comments by Reviewer 3}
\end{center}

The study "Application of a Cut-Cell Immersed Boundary Method for Wildfire Simulation over Complex Terrain" describe a method to consider the forcing induced by a complex topography in wildfire propagation within the framework of "physical models", combining different approach.

The work is undoubtedly well structured and seems the fruit of great number of years of serious work, so substantially I have nothing to point out. But from a formal point of view, in my opinion, it shows some aspect that should be improved. Here I suggest some observation to work upon.

1)	INTRODUCTION

Should be outlined where ``the state of the art'' and the bibliography analysis end, and where it starts the new work.

Given that some aims of this study are "fast simulation and outdoor fires" I would recommend to cite
the ``mass-consistent'' approach, ( for example the article Wagenbrenner, NS, Forthofer, JM, Lamb, BK, Shannon, KS, Butler, BW, (2016) Downscaling surface wind predictions from numerical weather prediction models in complex terrain with WindNinja. Atmos. Chem. Phys. 16:5229-5241, doi:10.5194/acp-16-5229-2016) and an "mass-consistent" application to a Rothermel/level set approach (Arca Bachisio, Ghisu Tiziano, Casula Marcello, Salis Michele, Duce Pierpaolo (2019) A web-based wildfire simulator for operational
applications. International Journal of Wildland Fire 28, 99-112. https://doi.org/10.1071/WF18078)

\hl{An additional paragraph has been added to the introduction that provides a reference to the review of models given in Arca et al. (2019) and provides some context on how the FDS suite of models differs from other approaches.}

2) MATHEMATICAL MODEL

The description of the mathematical model is too short. It is not possible to be clear in 30 lines for such a complex model. There is the risk of making a collection of citations and references to another series of works, while there should be an understandable basic outline.

Please provide at least a simple description of the phenomena that is going to be modelled, together with the model hypothesis that allow for the simplification of the general physical frame. For example, at least the kind of fuels and the transformation process involved in combustion should be briefly described. It would be important also to provide a short description of the single term of each equation and its derivation. For example, to understand the model and to have a ready legibility it is important to specify as (p-po)*g*l/p is the buoyancy term.

\hl{Defined explicitly the buoyancy term.}

The statement ``derived by factoring the divergence from the sensible enthalpy equation and applying the ideal gas law'' is difficult to understand. Therefore a few words should be dedicated.

\hl{We include Equation (3) is derived by factoring the divergence85from the sensible enthalpy equation and applying the ideal gas law.}

63: ``realizability'' is an important topic that should be described a little.

\hl{We added after equations(1)-(2) : Mass fractions $Y_\alpha$, solution of equations (1), must obey realizability constraints $0<Y_\alpha<1$ and $\sum_\alpha Y_\alpha=1$. In equations (1) starting from a realizable solution, realizability implies $\sum_\alpha \mathbf{J_{d}}_\alpha = 0$.}

64: Please describe the phenomena ``volumetric combustion'' and ``subgrid particle gassification''

\hl{We added : The volumetric combustion source term for species $\alpha$ is $\dot{m}_\alpha'''(\mathbf{x},t)$  and $\dot{m}_{b,\alpha}'''$ is the contribution to species $\alpha$ from subgrid particle gasification. These correspond to the amount of mass per unit volume and time of species $\alpha$ being added or substracted in a given point $\mathbf{x}$ due to chemical reaction or gasification of solid particles (or droplets), respectively.}

66: ``an ambient density'' is too vague. Please specify. 
\hl{We added : $\rho_0(z)$ is the modeled height dependent background density of the atmosphere.}

67: Please supply a few words about the physical phenomena ``fb is the particle force term.''

\hl{We changed the statement to : $\mathbf{f}_{b}$ is the term contributed by modeled particle drag forces.}

Eq. (3): $w$ is not defined. Please supply the definition.

\hl{We added : Also, $\boldsymbol{\omega}$ refers to the vorticity field.}

76: What is the meaning of ``thermodynamic divergence'' in the superscript of the RHS of the energy conservation equation? Is the thermodynamic divergence different from a normal divergence?

\hl{A velocity divergence, $\nabla\cdot\mathbf{u}$, can be factored out of every transport equation.  Of course, in order for the fomulation to be consistent, each divergence must be the same.  In a typical low-speed flow algorithm for solving the Navier-Stokes equations, a target divergence is prescribed from thermodyanmics.  Often, for simplicity, the flow is considered ``divergence free'' if constant density is a reasonable approximation.  In that case, the target ``thermodynamic divergence'' is implied to be zero. The algorithm then uses a \emph{projection scheme} to enforce this constraint (this is the purpose of solving the Poisson equation for the pressure). With variable density combustion codes, the divergence is more complicated.  The target thermodynamic divergence is computed from the sensible enthalpy equation, utilizing mass conservation and the ideal gas equation of state. Again, the projection scheme enforces this constraint.  After projection, all the transport equations share the same divergence, as must be true for consistency.  Further, the sensible enthalpy equation has been satisfied, which accounts for the important effects of heat transfer and dilatation from the combustion.}

3) TERRAIN DESCRIPTION AN DISCRETIZATION

Other important concept are only cited but not described at all, please some word should be spend to describe :

2 lines before eq. (7) ``a normal probe approach''

\hl{We added : Also, a normal probe approach is employed to sample information from the fluid to define fluxes in boundary cut-faces. In a normal probe method, an external point is defined at a normal distance from the body of the order of the Cartesian grid size. Then, information from the fluid at this external point is obtained via interpolation. }

line 96: ``flux-limited interpolation'' 
line 96: ``Godunov interpolation''

\hl{We reorganized the paragraph : In the cut-cell region a Godunov flux limited interpolation for the advective term is used. Flux limited interpolation is one of the fundamental components of stable numerical schemes for hyperbolic systems, of which mass transport inherits its mathematical properties.}

line 97: ``Runge-Kutta method''

\hl{We added : Explicit Runge-Kutta time integration methods are single-step multistage schemes widely used for advancing ordinary and partial differential equations [Leveque2007].}

\hl{Marcos,Randy}

\end{document}
